---
title: "Homework 7: Strings + Logical Vectors (Graphical Perception)"
author: "MICR 475/575"
format:
  html:
    toc: true
    embed-resources: true
execute:
  warning: false
  message: false
editor: visual
---

## Instructions

In this homework you will practice:

-   importing a Google Forms CSV export
-   working with **strings**
-   building and using **logical vectors**
-   making data tidy with `pivot_longer()`
-   making a simple **box plot**

You will work with a Google Forms CSV export from our in-class graphical perception experiment.

------------------------------------------------------------------------

## Setup

```{r}
library(tidyverse)

csv_path <- "../data/handb_ptest.csv"   # <-- update if needed
```

------------------------------------------------------------------------

# Q1. Import the data

**Task:** Read the CSV into an object called `raw`, then preview it.

```{r}
# YOUR CODE HERE
```

------------------------------------------------------------------------

# Q2. Tidy the data (Method A: pivot_longer first, then fix chart_type)

In the raw Google Forms export, the response columns have long names that include the full question text. Your goal is a tidy data frame with **one row per response**, and columns:

-   `timestamp`
-   `chart_type` (values like `T1`, `T2`, ..., `T9`)
-   `percent` (numeric)

**Task A:** Start from `raw`, rename `Timestamp` to `timestamp`, then `pivot_longer()` everything *except* `timestamp`.

**Task B:** Convert the `percent` column to a number.

**Task C:** Use **string operations** (and at least one **logical vector**) to convert the messy `chart_type` column into clean labels `T1` ... `T9`.

> Hint 1: `parse_number(chart_type)` can pull the number out of the string.\
> Hint 2: Google Forms sometimes uses odd numbering (1, 3, 5, ...) if the form had extra hidden questions.\
> Hint 3: A logical vector can help you keep only the question numbers you want.

**Task D:** Make a **box plot** of `percent` by `chart_type` (no log transform).

```{r}
# YOUR CODE HERE
```

------------------------------------------------------------------------

# Q3. Tidy the data (Method B: rename columns first, then pivot_longer)

This method uses the idea that (after `Timestamp`) the remaining columns are the 9 chart types, in order.

**Task A:** Create a new data frame `df` that keeps `timestamp` plus the 9 response columns.

**Task B:** Rename the 9 response columns to `T1` ... `T9` (keep `timestamp` as-is).

**Task C:** `pivot_longer()` to make a tidy data frame with `timestamp`, `chart_type`, `percent` (numeric).

**Task D:** Make the same **box plot** of `percent` by `chart_type`.

```{r}
# YOUR CODE HERE
```

------------------------------------------------------------------------

# Q4. Do the two methods agree?

**Task A:** Check that the boxplots from Q2 and Q3 are the same.

**Task B:** In 3–6 sentences, comment on what the box plots show. Which chart types look most vs least accurate in our class data?

```{r}
# YOUR CODE HERE
```
